Flexibility of interactions depends on habitat suitability

### 2019-08-08 paper/manuscript.Rmd
Add basic results

>>>>

We found a positive association between environmental suitability and the niche breath. 
This relationship was maintained when we account for the overall generality of a species and even in extremely conservative model parametrization when we include the number of possible interacting species as an independent variable. 
We define "possible" interacting species as one with which the species interacts in any of our ecological communities.

No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.

Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.

```
Call:
glm(formula = n_partners ~ scale(suitability) * guild, family = "poisson", 
    data = .)

Coefficients:
                               Estimate Std. Error z value Pr(>|z|)    
(Intercept)                     1.79092    0.02360  75.886  < 2e-16 ***
scale(suitability)              0.07750    0.02454   3.158  0.00159 ** 
guildpla_id                     0.64345    0.04361  14.756  < 2e-16 ***
scale(suitability):guildpla_id  0.07645    0.03631   2.106  0.03524 *  
---
AIC: 3739.6
```

```
Call:
glm(formula = n_partners ~ scale(suitability) * guild + scale(log(n_partners_global)), 
    family = "poisson", data = .)

Coefficients:
                               Estimate Std. Error z value Pr(>|z|)    
(Intercept)                     1.70709    0.02541  67.172  < 2e-16 ***
scale(suitability)              0.17021    0.02481   6.860 6.88e-12 ***
guildpla_id                     0.61872    0.04378  14.132  < 2e-16 ***
scale(log(n_partners_global))   0.42074    0.01970  21.362  < 2e-16 ***
scale(suitability):guildpla_id -0.02134    0.03657  -0.584     0.56    
---

AIC: 3302.1
```

```
Call:
glm(formula = n_partners ~ scale(suitability) * guild + scale(log(n_partners_global)) + 
    scale(n_possible_partners), family = "poisson", data = .)

Coefficients:
                               Estimate Std. Error z value Pr(>|z|)    
(Intercept)                    1.667769   0.025701  64.892  < 2e-16 ***
scale(suitability)             0.088729   0.024121   3.679 0.000235 ***
guildpla_id                    0.423815   0.043904   9.653  < 2e-16 ***
scale(log(n_partners_global))  0.138837   0.022829   6.082 1.19e-09 ***
scale(n_possible_partners)     0.351851   0.008547  41.167  < 2e-16 ***
scale(suitability):guildpla_id 0.010224   0.036728   0.278 0.780718    
---

AIC: 2141.5
```
